### 2018-07-16 paper/security-discussion.tex
adding to discussion, section on alternatives, related work framing
Adds security discussion of Sphinxes

\dots

@@

>>>>

There are two changes that we have made that must be analysed.
We changed the key agreement from a pure \ac{DHKE}, \ie based on the \ac{DH} 
assumption, to one containing an indirection.
We also changed from the classical \ac{OR} of a fixed path with one node per 
layer to \ac{POR} with several nodes per layer.

The confidentiality of the key previously rested entirely on the \ac{DH} 
assumption (\(\alpha\) in the header).
Now it also rests on the security of the \ac{PRP} \(\prp'\) (\(C\) in the 
header).
The integrity is still reduced to the security of the \ac{MAC} \(\mac\) 
(\(\gamma\) in the header).

The second change is that we use several nodes per layer as opposed to only 
one.
The proofs of Sphinx rests on the results of \textcite{CLOnionRouting}, which 
are results for ordinary \ac{OR} with only one node per layer.
As long as we output all the nodes in the next layer, the proofs should not 
change.
We note that this is actually quite natural as a malicious adversary can drop 
any incoming traffic to a router and wait for the timeout and retransmission to 
the next node.
As such, the adversary can learn all nodes in the layer.

With these arguments, we believe that Sphinxes inherits the \ac{UC} security 
properties of Sphinx, however, this should be formally analysed.

@@

\sonja{Failure, exception handling, such as reordered chunks, chunks
  on different devices, squad devices going offline during transfer}

\section{Alternatives}%
\label{Alternatives}

\subsection{Stateful \name}
\subsection{Beyond file exchange} web browsing, hidden services,
interaction and collaboration.
\subsection{Other predictions} time of day?
